A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-13 manuscript.Rmd
all figures now using include_graphics from knitr

The first line can be interpreted as follows: To create `analysis.pdf` (the first target in the file), the file `analysis.Rmd`, which depends on `data/clean.csv`, needs to be rendered. This dependency is itself a target (the second target in the file). To create `data/clean.csv`, `R/clean.R` and `data/iris.csv` are needed. If you type `make analysis.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/clean.csv` does not exist, Make creates it by executing the second target. Also, if one of the dependencies of a target is newer then the target itself, then Make updates everything that directly or indirectly depends on the target. Here, if `data\iris.csv` is newer then `data\clean.csv`, Make will attempt to recreate `data\clean.csv` first and then `analysis.pdf`. If there is a dependency which is missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which depends on everything. Then the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure 4).

![Build pane in RStudio](Images/build-pane.png)

>>>>

The first line can be interpreted as follows: To create `analysis.pdf` (the first target in the file), the file `analysis.Rmd`, which depends on `data/clean.csv`, needs to be rendered. This dependency is itself a target (the second target in the file). To create `data/clean.csv`, `R/clean.R` and `data/iris.csv` are needed. If you type `make analysis.pdf`, Make first checks whether the dependencies do exist and, if not, creates them. Here, if `data/clean.csv` does not exist, Make creates it by executing the second target. Also, if one of the dependencies of a target is newer then the target itself, then Make updates everything that directly or indirectly depends on the target. Here, if `data\iris.csv` is newer then `data\clean.csv`, Make will attempt to recreate `data\clean.csv` first and then `analysis.pdf`. If there is a dependency which is missing, and there is no target to make it, Make stops with an error message. It is a convention to have the first target named `all`, which depends on everything. Then the command `make` without any argument automatically creates everything possible in the project. The button `Build All` from within RStudio triggers this process (see Figure \@ref{fig:buildpane-rstudio}).

```{r buildpane-rstudio, fig.cap="Build pane in RStudio with access to Makefile target 'all'."}
knitr::include_graphics("Images/build-pane.png")
```
